It Is Unbearable To Breath Here': Air Quality, Open Incineration, And Misinformation In Blantyre, Malawi

### 2023-04-18 manuscript/manuscript.qmd
Fix email
Number fig and tbl labels

    email: kwangerlo@gmail.comm

@@

```{r}
#| label: tbl-peaks
#| tbl-cap: Peaks for both PM~2.5~ and PM~10~ are the number of data points above the WHO interim target 1 (annual) which is the least stringent; the number of observations recorded (count) is provided for reference.

@@

observations_location |> 
  left_join(no_peaks_who) |> 
  knitr::kable()
```

@@

```{r}
#| label: fig-24-hour-average
#| fig-cap: Average 24-hour PM~10~ and PM~2.5~ at 8 monitoring stations over 2 months
#| fig-align: center

@@

@@

```{r}
#| label: fig-pm-ratios
#| fig-cap: PM~10~:PM~2.5~ values for each location. Each line shows the minimum and maximum ratio for the day based on ratios calculated hourly. Does not include 14th to 16th October at location uMoyo due to extreme outliers.
#| fig-align: center

@@

@@

```{r}
#| label: fig-percent-exposure
#| fig-cap: Percentage of measured values categorised according to WHO 2021 targets
#| fig-align: center
#| fig-height: 5

@@

@@

```{r}
#| label: fig-five-minute-intervals
#| fig-cap: PM~2.5~ and PM~10~ values collected every 5 minutes over 10 months at 8 locations.
#| fig-align: center

>>>>

    email: kwangulero@gmail.com 

@@

```{r}
#| label: tbl01-peaks
#| tbl-cap: Peaks for both PM~2.5~ and PM~10~ are the number of data points above the WHO interim target 1 (annual) which is the least stringent; the number of observations recorded (count) is provided for reference.

@@

tbl01_peaks <- observations_location |> 
  left_join(no_peaks_who)

tbl01_peaks |> 
  write_csv(file = here::here("data/processed-data/tbl01-peaks.csv"))

tbl01_peaks |> 
  knitr::kable()

@@

```{r}
#| label: fig03-24-hour-average
#| fig-cap: Average 24-hour PM~10~ and PM~2.5~ at 8 monitoring stations over 2 months
#| fig-align: center

@@

dat_in_sum_day |> 
  write_csv(here::here("data/processed-data/fig03-24-hour-average.csv"))

@@

```{r}
#| label: fig04-pm-ratios
#| fig-cap: PM~10~:PM~2.5~ values for each location. Each line shows the minimum and maximum ratio for the day based on ratios calculated hourly. Does not include 14th to 16th October at location uMoyo due to extreme outliers.
#| fig-align: center

@@

dat_in_ratios |> 
  write_csv(file = here::here("data/processed-data/fig04-pm-ratios.csv"))

@@

```{r}
#| label: fig05-percent-exposure
#| fig-cap: Percentage of measured values categorised according to WHO 2021 targets
#| fig-align: center
#| fig-height: 5

@@

percent_exposure |> 
  write_csv("data/processed-data/fig05-percent-exposure.csv")

@@

```{r}
#| label: figA1-five-minute-intervals
#| fig-cap: PM~2.5~ and PM~10~ values collected every 5 minutes over 10 months at 8 locations.
#| fig-align: center
